Co-moving stars in \textsl{Gaia DR1}

### 2016-11-17 paper/ms.tex
Use macro for consistent symbol of dvtan

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/likelihoodratios.pdf}
  \end{center}
  \caption{%
    Left: Density histogram of likelihood ratios for candidate pairs and random pairs.
    Along with the distribution for the entire candidate pairs (black thick line),
    we show the distribution for subsets in slices of $\Delta v_t$.
    Right: $\Delta v_t$ vs separation in slices of $\ln \mathcal{L}_1 /\mathcal{L}_2$.
    \label{fig:likelihoodratios}}
    \vspace{1em}
\end{figure*}

Figure~\ref{fig:likelihoodratios} shows the likelihood ratios for all
$\sim 271$k initial pairs examined.
As discussed in \sectionname~\ref{sec:data}, we expect a correlation between likelihood
ratios of pairs, and their distribution in $\Delta v_t$ vs separation plane.
Specifically, as we sweep through from small $\Delta v_t$ to large, we expect
the population of pairs to change from genuinely co-moving to random.
This becomes clear when we look at the distribution of likelihood ratios for
slices of $\Delta v_t$ centered at 0.5, 5, and 9.5~\kms.
\todo{Fix in below and in the figure, $\Delta v_t$ should be $|\Delta v_t|$}
Pairs with $|\Delta v_t-0.5|<0.5$ are most likely actual co-moving pairs, and
their likelihood distribution is narrowly peaked above 6.
The distribution peaks at lower values and gets broader as $\Delta v_t$ increases,
and the number of random pairs increasingly dominate.
On the right panel of Figure~\ref{fig:likelihoodratios}, we show
how the distribution of pairs on $\Delta v_t$ vs separation plane changes
with decreasing $\ln \mathcal{L}_1 /\mathcal{L}_2$ ratios.
This is in agreement with our discussion in \sectionname~\ref{sec:data}.
Finally, as a test,
we compute the likelihood ratios for 200,000 random pairs of stars with the same
parallax signal-to-noise ratio cut as candidate pairs ($S/N > 8$).
Shown as gray shaded histogram in Figure~\ref{fig:likelihoodratios},
this distribution peaks at a much lower value ($\approx 2$),
and is clearly separated from highly probable co-moving pairs.

>>>>

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/likelihoodratios.pdf}
  \end{center}
  \caption{%
    \todo{
    Left: Density histogram of likelihood ratios for candidate pairs and random pairs.
    Along with the distribution for the entire candidate pairs (black thick line),
    we show the distribution for subsets in slices of $\Delta v_t$.
    Right: $\Delta v_t$ vs separation in slices of $\ln \mathcal{L}_1 /\mathcal{L}_2$.}
    \label{fig:likelihoodratios}}
    \vspace{1em}
\end{figure*}

Figure~\ref{fig:likelihoodratios} shows the likelihood ratios for all
$\sim 271$k initial pairs examined.
As discussed in \sectionname~\ref{sec:data}, we expect a correlation between likelihood
ratios of pairs, and their distribution in \absdvtan\ vs separation plane.
Specifically, as we sweep through from small \absdvtan\ to large, we expect
the population of pairs to change from genuinely co-moving to random.
This becomes clear when we look at the distribution of likelihood ratios for
slices of \absdvtan\ centered at 0.5, 5, and 9.5~\kms.
Pairs with $|\absdvtan -0.5|<0.5$ are most likely actual co-moving pairs, and
their likelihood distribution is narrowly peaked above 6.
The distribution peaks at lower values and gets broader as \absdvtan\ increases,
and the number of random pairs increasingly dominate.
On the right panel of Figure~\ref{fig:likelihoodratios}, we show
how the distribution of pairs on \absdvtan\ vs separation plane changes
with decreasing $\ln \mathcal{L}_1 /\mathcal{L}_2$ ratios.
This is in agreement with our discussion in \sectionname~\ref{sec:data}.
Finally, as a test,
we compute the likelihood ratios for 200,000 random pairs of stars with the same
parallax signal-to-noise ratio cut as candidate pairs ($S/N > 8$).
Shown as gray shaded histogram in Figure~\ref{fig:likelihoodratios},
this distribution peaks at a much lower value ($\approx 2$),
and is clearly separated from highly probable co-moving pairs.
